Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Make a less strong assertion after Hopcroft-Ullman definition.
paper.tex: Note Goldreich's definition also does not yield the exponential speedup.

Therefore, with this restriction,
we lose the apparent exponential speed up in computation time%
\footnote{
    It is ``apparent'' in the sense that,
    if $\P \neq \NP$,
    we will have this exponential slowdown in some problems
    when moving from nondeterministic to deterministic machines.
}
we have when using nondeterminism.
The following definitions we will see
does not suffer from this problem.

@@

>>>>

Therefore, with this restriction,
we lose the apparent exponential speed up in computation time%
\footnote{
    It is ``apparent'' in the sense that,
    if $\P \neq \NP$,
    we will have this exponential slowdown in some problems
    when moving from nondeterministic to deterministic machines.
}
we have when using nondeterminism.
We thus will analyze the following models
to see whether they also suffer from this problem.

@@

At least partially,
we can compute the characteristic function of the satisfiability problem
in linear time using this model.
The machine $M$ that will do the calculation will guess an assignment
and write $1$ if it is satisfying and write $\bot$ if it isn't.
This computes in linear time the function $f$, defined by
\begin{equation*}
    f(\varphi) = \begin{cases}
        1, & \text{if $\varphi$ is satisfiable.} \\
        \text{undefined}, & \text{if $\varphi$ is unsatisfiable.} \\
    \end{cases}
\end{equation*}
However,
this function falls short of being exactly $\SAT$'s characteristic function:
$f(\varphi)$ ought to be zero for unsatisfiable $\varphi$.
Although we cannot prove a strong assertion as
``if this works then $\P = \NP$'',
we can come close.

\begin{proposition}
    If there is a nondeterministic Turing machine
    that computes in polynomial time, according to Goldreich's definition,
    the characteristic function of the satisfiability problem,
    then $\NP = \coNP$.
\end{proposition}

($\NP = \coNP$ implies that $\NP = \PH$; that is,
the polynomial hierarchy collapses to the first level.)

\begin{proof}
    Suppose $M$ is the machine that computes $\SAT$'s characteristic function,
    under Goldreich definition, in polynomial time.

    To solve $\overline \SAT$,
    the complement of $\SAT$,
    using $\NP$ resources,
    create a nondeterministic machine $M'$ that will simulate $M$ on its input.
    On each branch, if $M$ returned either $\bot$ or $1$, reject;
    if $M$ returns $0$, accept.

    If the current instance is satisfiable,
    all branches will return either $\bot$ or $1$,
    so we are right in rejecting it;
    otherwise, if the current instance is unsatisfiable,
    at least some branch will return $0$,
    so we will correctly reject the input.

    Since the complement of $\SAT$ is $\coNP$-complete,
    any language in $\coNP$ can thus be solved with a nondeterministic machine;
    hence, $\coNP \subseteq \NP$.

    Similarly,
    every language $L$ of $\NP$ has a many-one reduction to $\SAT$;
    thus, the complement $\overline L$ has a many-one reduction
    to $\overline \SAT$.
    Hence, composing the reduction with the above algorithm
    that solves $\overline \SAT$ using a nondeterministic machine,
    we conclude that $\overline L \in \NP$.
    Thus, by definition, $L \in \coNP$.
    So, $\NP \subseteq \coNP$.

    This shows $\NP = \coNP$.
\end{proof}

Therefore, even though Goldreich's definition
yields an acceptable Gödel numbering,
it also have trouble in transposing the exponential speedup
we have using nondeterminism.
